---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# NYTimesArticleStock

The fluctuation in the stock market can be reflected and predicted through the most updated news. Triggered by this idea, this data project(package) helps to collect news data from the New York Times Archive API within a defined time period (from 1981 to current). The potential goal of creating this package is to find a method to collect and combine both sturctured (numerical) data from Yahoo Finance and unsturctured (text) data from NY Times together through web scraping data from APIs and text cleaning to get a decent format of merged data by TF-IDF.

## Installation

You can install NYTimesArticleStock from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("zj2213/NYTimesArticleStock")
```

## Load the package

```{r example}
library(NYTimesArticleStock)
```

To start with, you may required to register for a developer account on NY Times Api (see https://developer.nytimes.com/) and obtain an API key.

**key = [your API AS KEY]**


## References

https://developer.nytimes.com/archive_api.json
